Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2020-02-11 response_to_reviewers.tex

{\textbf{\large Response to Editor Vasconcelos}}

\rev{On technical advancement: the authors have made significant technical advances, as recognized by all three referees, however, the referees point out several technical points that could be better addressed (e.g., uncertainty analysis) in order to provide the credibility that the advances presented in this manuscript deserve. I leave it to the authors to decided how to address these points, e.g., either by restructuring the paper, incorporating additional studies/examples, or both.
}

\response{Uncertainty quantification is a long-standing challenge in seismic tomography that dates back to its inception. Checkerboard tests are basically useless (e.g., L\'ev\^eque, Rivera, and Wittlinger, 1993), and even ``proper'' tools, such as the resolution matrix suffer from the fact that ``resolution'' is controlled by playing with a subjective damping parameter. Bayesian
 inference would be a preferred method of inversion, but this is obviously not an option for the current study; an unavoidable fact that even Albert Tarantola grudgingly accepted.
Ideally, we would have tools that enable us to take multiple samples from the posterior model distribution, but unfortunately such tools have thus far eluded the community.
This is the reality in which the current study was conducted.

In this context we have tried, more so than other studies, to assess the quality of our model.
First, we calculate variance reductions for more than 20 million time windows and demonstrate quantitatively that M25 provides a significantly better fit to the data than both M15 and S362ANI.
We note at this point that ISC traveltime inversions often provide less than 10\% reductions in variance to \emph{only} P and S wave traveltimes (Nolet, personal communication).
Second, we present traveltime histograms for three-component measurements in four different passbands, and we demonstrate that the mean and standard deviations for model M25 are consistently reduced relative to M15 and S362ANI.
Finally, we use a held-out dataset of 320 earthquakes to demonstrate that these events, which were not used in the inversion, are fit equally well as the 1,480 events in the actual dataset (Incidentally, in this context, we find the comment by reviewer 2 that our paper lacks ``true scientific innovation'' insulting).
The original manuscript did not contain point-spread function (PSF) tests,
but four such tests are included in the revived manuscript.
A PSF test does not say much about uncertainty ---like checker-board tests and the resolution matrix--- but gives an idea of resolution and model parameter tradeoffs.
}

@@

\rev{On interpretation of the results: the reviewers commend the technical achievements of the authors, but are simply not convinced that the model obtained is a sufficient advancement on the authors previous model, in terms of providing new insight into Earth structure and/or composition.
Because this is a significant component of the current manuscript, the authors must decide how to best address these concerns: either by better supporting their interpretation with additional evidence (related to the previous point), or by choosing to write a new version that focuses on methodological tomography advances, and not so much on interpretation just yet (as suggested by reviewers).
}

\response{To say that the new model, GLAD-M25, is not a significant advancement over the previous model, GLAD-M15, is perplexing. First, we provide quantitative evidence in the forms of misfit reductions (Tables 1 \& 2) and traveltime \& amplitude histograms (Figs.~10, 11, 12, 14 \& 15 in the original manuscript) that M25 fits the data better than M15.
Second, M25 resolves numerous new features that were entirely missing in M15, such as the Fiji-Tonga slab near New Zealand, and various hotspots in the Atlantic and Indian oceans.
Finally, even a cursory look at the figures displaying the normalized power per angular degree clearly reveals an increase in power for GLAD-M25 relative to GLAD-M15 beyond degree~10 throughout the mantle.

In response to the reviews,
we have added a section (Section~7.1) which highlights the differences between GLAD-M15 and GLAD-M25,
and reduced the number of comparisons with other models, focusing on plumes and subduction zones instead.
}

### 2020-02-11 main.tex
update events_360.pdf
Updates from Overleaf

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_1480.pdf} \\
  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
  \caption{\small{(a) Distribution of 1,480~earthquakes used in this study. The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
  (b) Distribution of the 11,800~seismographic stations used in this study. Colors denote the number of events for which a given station contributes waveforms to the structural inversion. Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers. The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.
  \towenjie{Remove panels (b) and (c) and fix up the figure. Make sure the station count starts at 1, not 0.}
  }}
  \label{fig:eventsstations}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{\small{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 22~min 55~s--22~min 56~s time bin.
  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches computed for a surface focal depth are for identification purposes only.
  \towenjie{Relabel PS as PS+SP.}
  }}
  \label{fig:window_density_Z}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{\small{Summary of the held-out database containing 360 earthquakes. Theses events were not used in the structural inversion. (a) Distribution of events color coded by depth range as in Fig.~\ref{fig:eventsstations}(a). (b) \& (c) Histograms of moment magnitude and depth.}}
  \label{fig:events_360}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.8\textwidth]{figures/south_america.pdf}
\caption{\small{Contour plot (left) and cross-sections at various depths (right) of subduction underneath South America, showing improvements in resolution in GLAD-M25 compared to GLAD-M15.
The contour plot shows positive perturbations of vertically polarized shear wavespeeds in GLAD-M25. The ball in the contour plot denotes the 660~km discontinuity.}}
\label{fig:S_America}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{./figures/M24-Iceland.png}
  \caption{\small{Map views of vertically polarized shear-wave-speed perturbations in GLAD-M15 (top left) and GLAD-M24 (top right) underneath Iceland. Also shown are vertical cross-sections(bottom row) at the same location. As a primary hotspot, Iceland also becomes much more prominent in GLAD-M24, especially in the upper mantle. \towenjie{Please update.}
  }}
  \label{fig:M24-Iceland}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{./figures/M24-Reunion.png}
  \caption{\small{Map views at 250~km depth of vertically polarized shear-wave-speed perturbations in GLAD-M15 (left) and GLAD-M24 (right) at Indian Ocean. New features are emerging in GLAD-M24, as the hotspot at Reunion, Marion, Kerguelen, and Crozet just came out in GLAD-M24. \towenjie{Please update.} }}
  \label{fig:M24-Reunion}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/events_1480.pdf} \\
  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
  \caption{\small{(a) Distribution of 1,480~earthquakes used in this study. The color of each beach ball reflects its depth range, where blue designates events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km.
  (b) Distribution of the 11,800~seismographic stations used in this study. Colors denote the number of events for which a given station contributes waveforms to the structural inversion. Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers. The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.
  }}
  \label{fig:eventsstations}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{\small{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 22~min 55~s--22~min 56~s time bin.
  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches computed for a surface focal depth are for identification purposes only.
  }}
  \label{fig:window_density_Z}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{\small{Summary of the held-out database containing 360 earthquakes. Theses events were not used in the structural inversion. (a) Distribution of events color coded by depth range as in Fig.~\ref{fig:eventsstations}(a). (b) \& (c) Histograms of moment magnitude and depth. \tojeroen{Do I need to update this figure, to remove subfigure b and c?} }}
  \label{fig:events_360}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.8\textwidth]{figures/south_america.pdf}
\caption{\small{Contour plot (left) and cross-sections at various depths (right) of subduction underneath South America, showing improvements in resolution in GLAD-M25 compared to GLAD-M15.
The contour plot shows positive perturbations of vertically polarized shear wavespeeds in GLAD-M25. The ball in the contour map denotes the 660~km discontinuity.}}
\label{fig:S_America}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/M25-Iceland.pdf}
  \caption{\small{Map views of vertically polarized shear-wave-speed perturbations in GLAD-M15 (top left) and GLAD-M25 (top right) underneath Iceland. Also shown are vertical cross-sections(bottom row) at the same location. As a primary hotspot, Iceland also becomes more prominent in GLAD-M25, especially in the upper mantle.
  }}
  \label{fig:M24-Iceland}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/M25-Reunion.pdf}
  \caption{\small{Map views at 250~km depth of vertically polarized shear-wave-speed perturbations in GLAD-M15 (left) and GLAD-M25 (right) in the Indian Ocean. New features have emerged in GLAD-M25, such as the R\'eunion, Marion, Kerguelen, Maldives, Seychelles, Cocos, and Crozet hotspots.}
  }
  \label{fig:M24-Reunion}
\end{figure}
